### 2022-04-24 background.tex
Update methodology and add references

>>>>

To extract target speaker's voice from the mixed utterance, we first need to extract the information of the target speaker.
One common way is to use a vector to represent target speaker's information, and we call it the speaker embedding.
There are many ways and many different speaker embeddings, such as i-vector in~\cite{i-vector}, a speaker embedding based on end-to-end neural network in~\cite{deep_speaker}, x-vector in~\cite{x-vector}, d-vector in~\cite{d-vector}.

\subsubsection{Frequency-domain methods}

\subsubsection{Time-domain methods}
